### 2017-04-02 paper/sections/Formalization.tex
Small fix.
More.

\begin{figure*}[htbp]
\begin{mathpar}
	\framebox{$ e \rightarrow v $} \hspace{.5in}
	\sinvk \\
	\spathinvk \\
	\ssuperinvk
\end{mathpar}
\caption{Small-step semantics.}\label{fig:smallstep}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{mathpar}
	\creceiver \hspace{.5in}
	\red{\cpathreceiver} \\
	\red{\cargs} \\
	\red{\cpathargs} \\
	\red{\csuperargs} \\
	\cstatictype \\
	\cfreduce \\
	\cannoreduce
\end{mathpar}
\caption{Congruence. \haoyuan{How are the last two rules used?}}\label{fig:congruence}
\end{figure*}

@@

@@

	\inferrule* [left=]
	{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \; m \in dom(K) \} }
	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
			\end{tabular}}\right.}
	\inferrule* [left=]
		{ set = \; $\{$ K >: I \; | \; m \in dom(K) \} }
		{\mostSpecific_2(m, I) = prune(set)}

	\inferrule* [left=]
		{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \;
			\kwinterface \; K \; \kwextends \; \overline{K} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
			\kwoverride \; J \ldots \}  $\}$ }
		{\mostSpecific_3(m, I, J) = prune(set)}

@@

	\inferrule* [left=]
	{   \interface{I}{I}{M}
		\\ J \in \overline{I} }
	{\ext(I, J)}
	\end{mathpar}
	\caption{Auxiliary functions.}\label{fig:auxfunc}
\end{figure*}

@@

$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method lookup function.
We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
accurately, its parameters, returned expression and the types.

>>>>

\begin{figure*}[htbp]
\begin{mathpar}
	\sinvk \\
	\spathinvk \\
	\ssuperinvk
\end{mathpar}
\caption{Small-step semantics.}\label{fig:smallstep}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{mathpar}
	\creceiver \hspace{.5in}
	\red{\cpathreceiver} \\
	\red{\cargs} \\
	\red{\cpathargs} \\
	\red{\csuperargs} \\
	\cstatictype \\
	\cfreduce \\
	\cannoreduce
\end{mathpar}
\caption{Congruence.}\label{fig:congruence}
\end{figure*}

@@

To make our formalization concise and expressive, we have defined a list of
auxiliary functions, collected by Figure~\ref{fig:auxfunc}. To begin with, we
introduce the basic functions: $\ext, \updateSet$ and $\prune$. $\ext(I, J)$
simply indicates that interface $I$ directly extends interface $J$. Corresponding
to this is a more general case $I <: J$, meaning that $I$ is a subtype of $J$.
$\updateSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
in their signatures. Notice that $\updateSet(I, I)$ is a special representative of
the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
types, and filters out those that have subtypes in the same set. Finally in the returned set,
none of them has a subtyping to one another, since all super types have been removed.

@@

	\inferrule* [left=]
	{ set = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} }
	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
			\end{tabular}}\right.}
	\inferrule* [left=]
		{ set = \; \{ K >: I \; | \; m \in \updateSet(K, K) \} }
		{\mostSpecific_2(m, I) = prune(set)}

	\inferrule* [left=]
		{ set = \; \{ K <: J \; $and$ \; K >: I \; | \;
			m \in \updateSet(K, J)  \} }
		{\mostSpecific_3(m, I, J) = prune(set)}

@@

	\inferrule* [left=]
	{   \interface{I}{I}{M}
		\\ J \in \overline{I} }
	{\ext(I, J)}

	\inferrule* [left=]
	{   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
		\kwoverride \; J \ldots \} }
	{m \in \updateSet(I, J)}
	\end{mathpar}
	\caption{Auxiliary functions.}\label{fig:auxfunc}
\end{figure*}

@@

$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
accurately, its parameters, returned expression and the types.
